Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-08-29 paper/paper.tex
save

\textit{Combined best settings.} When all best settings are combined (\ie,
Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance reaches  $0.9862$, combining the high recall of NYSIIS blocking
with the better precision of Random Forests.

>>>>

\textit{Combined best settings.} When all best settings are combined (\ie,
Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance reaches $0.9862$, \ie, the best of all reported results. In particular,
this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
and the high precision of Random Forests.
